\input{./._relpath-to-latexroot.ltx}
\documentclass[\latexroot/\projectname]{subfiles}
\input{\latexroot/@resources/subfile-setup.ltx}

\begin{document}

\section{Introduction}
\whenintegrated{\label{sec:intro}} % integrated doc: SST for labels
\setcounter{page}{0}\pagenumbering{arabic}

Who holds government debt is central to macroeconomic stability. The distribution of debt across domestic banks, domestic non-banks, and foreign investors shapes default incentives, financial repression, and the transmission of fiscal shocks. Yet most models of sovereign debt focus on the total level of debt and treat its composition as exogenous.

This paper develops a simple framework in which the composition of government debt is endogenously determined by borrowing constraints and repression costs. The government faces default limits on domestic and foreign non-bank creditors, while accumulating debt in the banking sector generates convex financial repression costs. These constraints define a no-default region in debt space and imply threshold effects: beyond a critical level of total debt, the government exhausts non-bank borrowing capacity and reallocates marginal debt to banks.

We structurally estimate the model using panel data on debt composition across countries and over time. The estimation identifies distinct borrowing limits across creditor types and provides a tractable framework to interpret variation in who holds government debt.

% Smart bibliography: Only include bibliography if standalone AND has citations
\smartbib

\end{document}
